Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-10-28 accessPEP.Rmd
deleting ttimes plot code

## Files
source("R/utils.R")
source("R/models.R")
source("R/data_functions.R")
source("R/get.burden.R")
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, 
                      include = TRUE, cache.lazy = FALSE)
```

>>>>

## Files
source("R/utils.R")
source("R/models.R")
source("R/data_functions.R")
source("R/get.burden.R")
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, 
                      include = TRUE, cache.lazy = FALSE)

##### Getting raster of coverage
ctar_metadata <- read.csv("data/ctar_metadata.csv")
